\documentclass[12pt]{article}
\usepackage[ a4paper, total={8.1in, 11.5in}]{geometry}
\title{\textbf{EVOLUTION OF MODERN HEALTH CARE}}
\author{By Harsh Agrawal, 21111021}
\date{}
\begin{document}
\maketitle
\raggedright{\section{\underline{What is Health Care (Definition):}}}
Healthcare Is the \textbf{prevention, treatment, and management of illness} and the preservation of mental and physical well-being through the services offered by the medical, nursing, and allied health professions.
\newline
\section{\underline{Modern Health Care:}}
Modern Health Care is the development and innovation in the health care system by means of emerging technologies and facilities.
\newline
\section{\underline{Some Problems faced by Health Care System:}}
\begin{itemize}
\item Lack of proper Diagnostic and treatment Equipment in some hospitals.
\item Costly and unaffordable treatments in Remote areas.
\item Lack of advanced facilities for faster working.
\item Lack of reach of medical facilities To all people
\item Lack in proper management of Hospitals and Facilities
\item Under-developed Treatment techniques.
\end{itemize}

\section{\underline{Evolution of Modern Health Care:}}
As the time emerges, it is the need of the hour to develop and modernize the Most important sector of our lives, i.e. The Health Care sector. There are a lot of problems faced by The health care system and people affected by it. The Evolution Of modern Health Care is developing and adapting the Newer Emerging Technologies and other innovative techniques in the health care sector. As the time passes we have witnessed a series of developments such as innovation of a wearable ECG Device, A handheld Ultrasound, and a lot more.

\subsection{\underline{Some Of The Emerging Technology Used In Modern Health Care System:}}
\begin{itemize}
\item \textbf{\underline{Semiconductors and Microchips}}-
\newline Semiconductors are used in almost all of the devices used in Medical care. The development in the semiconductors and innovation of microchips have added a lot more to making handy machines like a mini ultrasound and Improvisations of the MRI machines, etc. which can be used in remote areas for diagnosis. Further development using Nanotechnology can be made for making small, but the most efficient devices used in health care.
\item \textbf{\underline{Computer Science}}- 
\newline All the softwares are created using computer science. The development in this field has led to the building of new and efficient softwares for better diagnosis and treatments. They are also convenient to use.
\item \textbf{\underline{Artifical Technology and Machine Learning-}}
\newline The most emerging technology, AI and ML, is being used in almost all fields. In the health care sector, it is being used in developing medical devices that is easy and full of features for both patients and doctors. Artificial limbs are an innovation of AI with mechanics. AI and ML can be used to monitor real-time data of patients, increasing the accuracy of treatments. Uncountable developments can be made.
\item \textbf{\underline{Data Science-}}
\newline One of the problems we face is the lack of management in hospitals. Using data science, it is very easy to manage the records and data of patients in the hospitals. Using this, the management can track the patient’s condition, number of beds available, Stock of medicines and devices, Doctors are occupied or free, and management of staffs. This surely will increase the management of hospitals and medical stations.
\item \textbf{\underline{Cloud computing-}}
\newline  Cloud computing, is used to store a large number of data, wirelessly in a cloud service. Using this technology, it is easier to store the medical records of a patient, for better diagnosis and treatments. A patient’s previous detailed health records would be available at any time making it easier for doctors to treat
\end{itemize}
\centering{\textbf{\underline{Development of health care in remote and economically weak areas-}}}

\raggedright{ Medical services in the remote areas, is now getting easier as compared to previous times. The innovation of handheld and portable machines like ECG, Portable Ventilators, Portable Dialysis, CPR, is now available so as to carry them to remote areas.
Ambulances and Medically equipped vehicles are being developed with an Intensive Care Unit(ICU) on-the-go for emergency purposes. For cost efficient methods, many companies are now working on devices which are comparatively cheap and can be affordable by small hospitals and medical units in villages. Health insurances are now cheap and and easily accessible by people with cost benefits and better treatments. Government schemes also play a major role for Financially weak people to get proper medical facilities.}
\end{document}
